---
title: "Vigilant Asset Allocation Tests"
author: "Keith Berry"
date: "January 4, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---


# TODO 

X Calculate 30 day volatility and add plots of it 

Need to try with B = 2 as well and with leverage. Basic leverage and then some type of volatility based leverage

Try using the DAA canary portfolio with G4 

Try using longer term momentum to pick which Risk On Assets to prevent so much churn.... (3+6+12)? Or 12 months?  This looks like it might work, plot the values, so we can inspect, only switch assets when we clearly need to. 

Same with Risk Off? 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(knitr)
library(kableExtra)


con = gzcon(url('https://github.com/systematicinvestor/SIT/raw/master/sit.gz', 'rb'))
source(con)
close(con)

load.packages('quantmod')   
```

## Basic Vigilant Asset Allocation test

First version is the model exactly as described on TrendExplorer this is the VAA.G4.T1.B1 model.

```{r load-data, echo=FALSE}

models = list()

data <- readRDS("./data/raw-prices.RData")

bt.prep(data, align='remove.na')

prices = data$prices 

ret = bt.apply.matrix(prices, ROC, type='discrete')
abs.ret = abs(ret) * 100
abs.ret.average = bt.apply.matrix(abs.ret, SMA, 30)

plot(abs.ret.average[,spl("VOO,VEA,VWO")])

period.ends = endpoints(prices, 'months')

monthly.prices = prices[period.ends,]

m1.ret = monthly.prices/mlag(monthly.prices,1)-1
m3.ret = monthly.prices/mlag(monthly.prices,3)-1
m6.ret = monthly.prices/mlag(monthly.prices,6)-1
m12.ret = monthly.prices/mlag(monthly.prices,12)-1

f13612w = ((12*m1.ret+4*m3.ret+2*m6.ret+1*m12.ret)/4)*100

risky = spl("VOO,VEA,VWO,BND")
safe = spl("SHY,IEF,LQD")

top.risky = ntop(f13612w[,risky],1) 
risk.on = rowSums(f13612w[,risky] < 0)==0

risky.positions = top.risky * risk.on

top.safe = ntop(f13612w[,safe],1)
risk.off = rowSums(f13612w[,risky] < 0)>0

safe.positions = top.safe * risk.off

data$prices = data$prices[period.ends,]
data$weight = data$prices
data$weight[] = 0

positions = cbind(risky.positions,safe.positions)
positions$TLT = 0

data$weight = positions[,colnames(data$weight)]

models$vaa.g4.t1.b1 = bt.run.share(data, trade.summary=T, clean.signal=F)

currentModel = models$vaa.g4.t1.b1
#currentModel$equity=currentModel$equity["2000-08-31/"]
model.detail = bt.detail.summary(currentModel)
twelve.ret = ROC(currentModel$equity,12,type="discrete")
model.detail$System$Roll.TwelveM = (sum(twelve.ret > 0,na.rm=TRUE)/(sum(twelve.ret > 0,na.rm=TRUE)+sum(twelve.ret < 0,na.rm=TRUE)))*100

kable(list2matrix(model.detail)) %>% kable_styling()
plotbt.monthly.table(currentModel$equity)
kable(tail(currentModel$trade.summary$trades,24)) %>% kable_styling()
plot(currentModel$equity)
plot(compute.drawdown(currentModel$equity)*100)
# Need to align the pricing columns
```

Now with some leverage!!

```{r, echo=FALSE}

top.risky = ntop(f13612w[,risky],1) 
risk.on = rowSums(f13612w[,risky] < 0)==0

leverage = 1/abs.ret.average
leverage = 2 
#leverage$SHY = 1

#risky.positions = top.risky * risk.on * leverage[,risky]
risky.positions = top.risky * risk.on * 2

top.safe = ntop(f13612w[,safe],1)
risk.off = rowSums(f13612w[,risky] < 0)>0

#safe.positions = top.safe * risk.off * leverage[,safe]
safe.positions = top.safe * risk.off * 2

#data$prices = data$prices[period.ends,]
data$weight = data$prices
data$weight[] = 0

positions = cbind(risky.positions,safe.positions)
positions$TLT = 0

data$weight = positions[,colnames(data$weight)]

models$vaa.g4.t1.b1.l1 = bt.run.share(data, trade.summary=T, clean.signal=F)

currentModel = models$vaa.g4.t1.b1.l1
currentModel$equity=currentModel$equity["1997-04-30/"]
model.detail = bt.detail.summary(currentModel)
twelve.ret = ROC(currentModel$equity,12,type="discrete")
model.detail$System$Roll.TwelveM = (sum(twelve.ret > 0,na.rm=TRUE)/(sum(twelve.ret > 0,na.rm=TRUE)+sum(twelve.ret < 0,na.rm=TRUE)))*100

kable(list2matrix(model.detail)) %>% kable_styling()
plotbt.monthly.table(currentModel$equity)
plot(currentModel$equity)
plot(compute.drawdown(currentModel$equity)*100)
kable(tail(f13612w,13)) %>% kable_styling()
kable(list2matrix(tail(currentModel$trade.summary$trades,13))) %>% kable_styling()
kable(list2matrix(model.detail)) %>% kable_styling()
# Need to align the pricing columns
```

Now try the VAA G4 T2 B1 model 

```{r, echo=FALSE}

top.risky = ntop(f13612w[,risky],2) 
risk.on = rowSums(f13612w[,risky] < 0)==0

risky.positions = top.risky * risk.on

top.safe = ntop(f13612w[,safe],1)
risk.off = rowSums(f13612w[,risky] < 0)>0

safe.positions = top.safe * risk.off

#data$prices = data$prices[period.ends,]
data$weight = data$prices
data$weight[] = 0

positions = cbind(risky.positions,safe.positions)
positions$TLT = 0

data$weight = positions[,colnames(data$weight)]

models$vaa.g4.t2.b1 = bt.run.share(data, trade.summary=T, clean.signal=F)

currentModel = models$vaa.g4.t2.b1
#currentModel$equity=currentModel$equity["2000-08-31/"]
model.detail = bt.detail.summary(currentModel)
twelve.ret = ROC(currentModel$equity,12,type="discrete")
model.detail$System$Roll.TwelveM = (sum(twelve.ret > 0,na.rm=TRUE)/(sum(twelve.ret > 0,na.rm=TRUE)+sum(twelve.ret < 0,na.rm=TRUE)))*100

kable(list2matrix(model.detail)) %>% kable_styling()
plotbt.monthly.table(currentModel$equity)
plot(currentModel$equity)
plot(compute.drawdown(currentModel$equity)*100)
# Need to align the pricing columns
```
Now try the VAA G4 T3 B1 model 

```{r, echo=FALSE}

top.risky = ntop(f13612w[,risky],3) 
risk.on = rowSums(f13612w[,risky] < 0)==0

risky.positions = top.risky * risk.on

top.safe = ntop(f13612w[,safe],1)
risk.off = rowSums(f13612w[,risky] < 0)>0

safe.positions = top.safe * risk.off

#data$prices = data$prices[period.ends,]
data$weight = data$prices
data$weight[] = 0

positions = cbind(risky.positions,safe.positions)
positions$TLT = 0

data$weight = positions[,colnames(data$weight)]

models$vaa.g4.t3.b1 = bt.run.share(data, trade.summary=T, clean.signal=F)

currentModel = models$vaa.g4.t3.b1
#currentModel$equity=currentModel$equity["2000-08-31/"]
model.detail = bt.detail.summary(currentModel)
twelve.ret = ROC(currentModel$equity,12,type="discrete")
model.detail$System$Roll.TwelveM = (sum(twelve.ret > 0,na.rm=TRUE)/(sum(twelve.ret > 0,na.rm=TRUE)+sum(twelve.ret < 0,na.rm=TRUE)))*100

kable(list2matrix(model.detail)) %>% kable_styling()
plotbt.monthly.table(currentModel$equity)
plot(currentModel$equity)
plot(compute.drawdown(currentModel$equity)*100)
# Need to align the pricing columns
```

Now try with 6 month top asset VAA G4 T1 B1 model 

```{r, echo=FALSE}

top.risky = ntop(m6.ret[,risky],1) 
risk.on = rowSums(f13612w[,risky] < 0)==0

risky.positions = top.risky * risk.on

top.safe = ntop(m6.ret[,safe],1)
risk.off = rowSums(f13612w[,risky] < 0)>0

safe.positions = top.safe * risk.off

#data$prices = data$prices[period.ends,]
data$weight = data$prices
data$weight[] = 0

positions = cbind(risky.positions,safe.positions)
positions$TLT = 0

data$weight = positions[,colnames(data$weight)]

models$vaa.g4.t1.b1.m6 = bt.run.share(data, trade.summary=T, clean.signal=F)

currentModel = models$vaa.g4.t1.b1.m6
#currentModel$equity=currentModel$equity["2000-08-31/"]
model.detail = bt.detail.summary(currentModel)
twelve.ret = ROC(currentModel$equity,12,type="discrete")
model.detail$System$Roll.TwelveM = (sum(twelve.ret > 0,na.rm=TRUE)/(sum(twelve.ret > 0,na.rm=TRUE)+sum(twelve.ret < 0,na.rm=TRUE)))*100

kable(list2matrix(model.detail)) %>% kable_styling()
plotbt.monthly.table(currentModel$equity)
kable(tail(currentModel$trade.summary$trades,13)) %>% kable_styling()
plot(currentModel$equity)
plot(compute.drawdown(currentModel$equity)*100)
# Need to align the pricing columns
```

Now try the DAA canary universe 

```{r, echo=FALSE}

canary = spl("VWO,BND")

top.risky = ntop(f13612w[,risky],1) 
risk.on = rowSums(f13612w[,canary] < 0)==0

risky.positions = top.risky * risk.on

top.safe = ntop(f13612w[,safe],1)
risk.off = rowSums(f13612w[,canary] < 0)>0

safe.positions = top.safe * risk.off

#data$prices = data$prices[period.ends,]
data$weight = data$prices
data$weight[] = 0

positions = cbind(risky.positions,safe.positions)
positions$TLT = 0

data$weight = positions[,colnames(data$weight)]

models$daa.g4.t1.b1 = bt.run.share(data, trade.summary=T, clean.signal=F)

currentModel = models$daa.g4.t1.b1
#currentModel$equity=currentModel$equity["2000-08-31/"]
model.detail = bt.detail.summary(currentModel)
twelve.ret = ROC(currentModel$equity,12,type="discrete")
model.detail$System$Roll.TwelveM = (sum(twelve.ret > 0,na.rm=TRUE)/(sum(twelve.ret > 0,na.rm=TRUE)+sum(twelve.ret < 0,na.rm=TRUE)))*100

kable(list2matrix(model.detail)) %>% kable_styling()
plotbt.monthly.table(currentModel$equity)
kable(tail(currentModel$trade.summary$trades,24)) %>% kable_styling()
plot(currentModel$equity)
plot(compute.drawdown(currentModel$equity)*100)
# Need to align the pricing columns
```

Now try with just a two asset safe portfolio

```{r, echo=FALSE}

canary = spl("VWO,BND")
safe = spl("SHY,IEF")

top.risky = ntop(f13612w[,risky],1) 
risk.on = rowSums(f13612w[,canary] < 0)==0

risky.positions = top.risky * risk.on

top.safe = ntop(f13612w[,safe],1)
risk.off = rowSums(f13612w[,canary] < 0)>0

safe.positions = top.safe * risk.off

#data$prices = data$prices[period.ends,]
data$weight = data$prices
data$weight[] = 0

positions = cbind(risky.positions,safe.positions)
positions$TLT = 0
positions$LQD = 0

data$weight = positions[,colnames(data$weight)]

models$daa.g4.t1.b1.c2 = bt.run.share(data, trade.summary=T, clean.signal=F)

currentModel = models$daa.g4.t1.b1.c2
#currentModel$equity=currentModel$equity["2000-08-31/"]
model.detail = bt.detail.summary(currentModel)
twelve.ret = ROC(currentModel$equity,12,type="discrete")
model.detail$System$Roll.TwelveM = (sum(twelve.ret > 0,na.rm=TRUE)/(sum(twelve.ret > 0,na.rm=TRUE)+sum(twelve.ret < 0,na.rm=TRUE)))*100

kable(list2matrix(model.detail)) %>% kable_styling()
plotbt.monthly.table(currentModel$equity)
kable(tail(currentModel$trade.summary$trades,24)) %>% kable_styling()
plot(currentModel$equity)
plot(compute.drawdown(currentModel$equity)*100)
# Need to align the pricing columns
```
...and using T3 like in the paper

```{r, echo=FALSE}

canary = spl("VWO,BND")
safe = spl("SHY,IEF")

top.risky = ntop(f13612w[,risky],3) 
risk.on = rowSums(f13612w[,canary] < 0)==0

risky.positions = top.risky * risk.on

top.safe = ntop(f13612w[,safe],1)
risk.off = rowSums(f13612w[,canary] < 0)>0

safe.positions = top.safe * risk.off

#data$prices = data$prices[period.ends,]
data$weight = data$prices
data$weight[] = 0

positions = cbind(risky.positions,safe.positions)
positions$TLT = 0
positions$LQD = 0

data$weight = positions[,colnames(data$weight)]

models$daa.g4.t3.b1.c2 = bt.run.share(data, trade.summary=T, clean.signal=F)

currentModel = models$daa.g4.t3.b1.c2
#currentModel$equity=currentModel$equity["2000-08-31/"]
model.detail = bt.detail.summary(currentModel)
twelve.ret = ROC(currentModel$equity,12,type="discrete")
model.detail$System$Roll.TwelveM = (sum(twelve.ret > 0,na.rm=TRUE)/(sum(twelve.ret > 0,na.rm=TRUE)+sum(twelve.ret < 0,na.rm=TRUE)))*100

kable(list2matrix(model.detail)) %>% kable_styling()
plotbt.monthly.table(currentModel$equity)
#kable(tail(currentModel$trade.summary$trades,24)) %>% kable_styling()
plot(currentModel$equity)
plot(compute.drawdown(currentModel$equity)*100)
# Need to align the pricing columns
```

Try adding TLT back in lets use the T2 B1 

```{r, echo=FALSE}

safe = spl("SHY,IEF,TLT")
top.risky = ntop(f13612w[,risky],2) 
risk.on = rowSums(f13612w[,risky] < 0)==0

risky.positions = top.risky * risk.on

top.safe = ntop(f13612w[,safe],1)
risk.off = rowSums(f13612w[,risky] < 0)>0

safe.positions = top.safe * risk.off

#data$prices = data$prices[period.ends,]
data$weight = data$prices
data$weight[] = 0

positions = cbind(risky.positions,safe.positions)
positions$LQD = 0

data$weight = positions[,colnames(data$weight)]

models$vaa.g4.t2.b1.tlt = bt.run.share(data, trade.summary=T, clean.signal=F)

currentModel = models$vaa.g4.t2.b1.tlt
#currentModel$equity=currentModel$equity["2000-08-31/"]
model.detail = bt.detail.summary(currentModel)
twelve.ret = ROC(currentModel$equity,12,type="discrete")
model.detail$System$Roll.TwelveM = (sum(twelve.ret > 0,na.rm=TRUE)/(sum(twelve.ret > 0,na.rm=TRUE)+sum(twelve.ret < 0,na.rm=TRUE)))*100

```

```{r, echo=FALSE}
kable(list2matrix(model.detail)) %>% kable_styling()
plotbt.monthly.table(currentModel$equity)
plot(currentModel$equity)
plot(compute.drawdown(currentModel$equity)*100)
# Need to align the pricing columns
```

# Compare all portfolios

```{r, echo=FALSE}

kable(plotbt.strategy.sidebyside(models, make.plot=F, return.table=T)) %>% kable_styling()
      
```